Applying gamification to developer practices

### 2013-09-09 paper_id1.tex
adjusted pivot table on nav ratio

The other questions included whether they reviewed the training materials on structured navigation commands, installed the Sando code search tool, and what types of development tasks they would consider using structured navigation for in general.  A key demographic question is how well they know the code they work in rated from "I work in code that I wrote", "I maintain code that I am familiar with", to "I recently learned the code"

@@

Those who rated their knowledge of structured navigation commands highly, did better in the points and generally had a higher average navigation ratio than those who rated their prior knowledge lower.  This could indicate that using structure navigation is somewhat of a habit that takes longer to change.  There was also feedback that people wanted more information presented to them by the tool on what commands to use, so they may not have closed the knowledge gap during the pilot.

Those who worked in code that they wrote tended to use less structured navigation having a lower navigation ratio and point score.  Those who had recently learned the code they were working in had more consistent use of structured navigation and one of them used Sando the most of the pilot participants.

>>>>

The other questions included whether they reviewed the training materials on structured navigation commands, installed the Sando code search tool, and what types of development tasks they would consider using structured navigation for in general.  Another demographic question is how well they know the code they work in rated from "I work in code that I wrote", "I maintain code that I am familiar with", to "I recently learned the code"

@@

Those who rated their knowledge of structured navigation commands highly, did better in the points than those who rated their prior knowledge lower.  This could indicate that using structured navigation is somewhat of a habit that takes longer to change.  There was also feedback that people wanted more information presented to them by the tool on what commands to use, so they may not have closed the knowledge gap during the pilot.

Those who worked in code that they wrote tended to use less structured navigation having a lower navigation ratio.  Those who had recently learned the code they were working in had more consistent use of structured navigation and one of them used Sando the most of the pilot participants.
